Decompositions of congruence subgroups of Chevalley groups

### 2015-11-09 paper.tex
Fixed broken section names in pdfs

\subsection{$\K_1$-functor modeled on Chevalley groups}
Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).

>>>>

\subsection{\texorpdfstring{$\K_1$}{K1}-functor modeled on Chevalley groups}
Recall that by a theorem of Taddei $\E(\Phi, R)$ is a normal subgroup of $\G_{sc}(\Phi, R)$ provided $\Phi$ is an irreducible root system of rank $\geqslant 2$ (see~\cite{Ta}).
